Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-28 paper/ms.tex
Fixing table labels, captions

\begin{deluxetable*}{ccccccc}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within $250\,\pc$ of the Sun.}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} \\ \colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$}}f
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 & 352\tablenotemark{b} \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 & 410\tablenotemark{c} \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 & 112\tablenotemark{d} \\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 & 400\tablenotemark{e} \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 &  \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 & \\
NGC2451A\tablenotetext{a} & 193.7 & 5.8 & -1805 & 0.21 & 73.4 & \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 & \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9 & 550\tablenotemark{d}
\enddata

@@

\tablerefs{\citet{2018AA...616A..10G}}
\label{tab:real_clusters}
\end{deluxetable*}

@@

\begin{deluxetable*}{ccccccc}
\tablecaption{Description and names of the three orbits considered in this work.}
\tablehead{\colhead{name} & \colhead{initial position} & \colhead{initial
velocity} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$}\\ \colhead{ } &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{km}/\mathrm{s}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc}$}}
\startdata 
thin & $(8, 0, 0)$ & $(0, -190, 10)$ & 40.3 & -1520 & 0.69 & 0.12 \\
thick & $(8, 0, 0)$ & $(0, -190, 50)$ & 32.5 & -1520 & 23.0 & 0.85 \\ 
halo & $(8, 0, 0)$ & $(0, -190, 190)$ & 32.8 & -1520 & 529.1 & 6.16
\enddata
\label{tab:orbits}
\end{deluxetable*}

@@

\begin{deluxetable}{ccc}
\tablecaption{Stellar Disk Scale Heights}
\tablehead{\colhead{galaxy} & \colhead{thin disk} & \colhead{thick disk} \\ 
\colhead{} & \colhead{(pc)} & \colhead{(pc)} } 
\startdata
MW\tablenotemark{a} & 300 & 900 \\
m12i\tablenotemark{b} & 480 & 2000 \\
m12f\tablenotemark{b} & 440 & 1280 \\
m12m\tablenotemark{b} & 290 & 1030 \\
\enddata
% \tablerefs{\citet{2016ARAA..54..529B,2018arXiv180610564S,2008ApJ...673..864J}}

\tablenotetext{a}{\citet{2008ApJ...673..864J,2016ARAA..54..529B}}
\tablenotetext{b}{\citet{2018arXiv180610564S}}

\label{tab:scale_height}
\end{deluxetable}

>>>>

\begin{deluxetable*}{ccccccc}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} \\ \colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$}}f
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 & 352\tablenotemark{b} \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 & 410\tablenotemark{c} \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 & 112\tablenotemark{d} \\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 & 400\tablenotemark{e} \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 &  \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 & \\
NGC2451A\tablenotemark{a} & 193.7 & 5.8 & -1805 & 0.21 & 73.4 & \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 & \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9 & 550\tablenotemark{d}
\enddata

@@

\tablerefs{\citet{2018AA...616A..10G}}
\end{deluxetable*}

@@

\begin{deluxetable*}{ccccccc}
\tablecaption{Description and names of the three orbits considered in this
work.\label{tab:orbits}}
\tablehead{\colhead{name} & \colhead{initial position} & \colhead{initial
velocity} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$}\\ \colhead{ } &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{km}/\mathrm{s}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc}$}}
\startdata 
thin & $(8, 0, 0)$ & $(0, -190, 10)$ & 40.3 & -1520 & 0.69 & 0.12 \\
thick & $(8, 0, 0)$ & $(0, -190, 50)$ & 32.5 & -1520 & 23.0 & 0.85 \\ 
halo & $(8, 0, 0)$ & $(0, -190, 190)$ & 32.8 & -1520 & 529.1 & 6.16
\enddata
\end{deluxetable*}

@@

\begin{deluxetable}{ccc}
\tablecaption{Stellar disk scale heights of the real Milky Way and the
simulated galaxies considered in this work.\label{tab:scale_height}}
\tablehead{\colhead{galaxy} & \colhead{thin disk} & \colhead{thick disk} \\ 
\colhead{} & \colhead{(pc)} & \colhead{(pc)} } 
\startdata
MW\tablenotemark{a} & 300 & 900 \\
m12i\tablenotemark{b} & 480 & 2000 \\
m12f\tablenotemark{b} & 440 & 1280 \\
m12m\tablenotemark{b} & 290 & 1030 \\
\enddata
% \tablerefs{\citet{2016ARAA..54..529B,2018arXiv180610564S,2008ApJ...673..864J}}

\tablenotetext{a}{\citet{2008ApJ...673..864J,2016ARAA..54..529B}}
\tablenotetext{b}{\citet{2018arXiv180610564S}}
\end{deluxetable}
